A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-26 sections/Metatheory.tex
S4 Metatheory: some corollaries, synced with Abella script

\begin{corollary}[Soundness, single judgment form]

\end{corollary}

@@

\begin{theorem}[Completeness]
If \emph{wf }$\Gm$ and $\exists \Om$ s.t. $\Gm\sto\Om$ and $\Om\redto\nil$, then $\Gm \redto \nil$.
\label{thm:completeness}
\end{theorem}

@@

The following corollary is derived immediately from Theorem~\ref{thm:completeness}.
\begin{corollary}[Completeness, single judgment form]
\end{corollary}

@@

We have proven this theorem by a lexicographic group of induction measures\\
$\langle |\Gm|_e, |\Gm|_\Leftrightarrow, |\Gm|_\forall, |\Gm|_{\al}, |\Gm|_\to + |\Gm| \rangle$
on the worklist $\Gm$.
$|\cdot|_e$ and $|\cdot|_\Leftrightarrow$ measure the total ``size'' of teams
and the total ``difficulty'' of judgments, respectively;
$|\cdot|_\forall$ and $|\cdot|_\to$ count the total number of
universal quantifiers and function types, respectively;
$|\cdot|_{\al}$ counts the number of existential variables in the worklist.

@@

Combining all the three main results, we know that the declarative system is decidable,
with the help of our algorithm.
\begin{corollary}[Decidability of Declarative Typing]
\end{corollary}
\subsection{Abella}

>>>>

\begin{corollary}[Soundness, single judgment form]
Given \emph{wf }$\Psi$ and $\Gm = \Psi$:
\begin{enumerate}
    \item If $\Gm \Vdash A \le B \redto \nil$ then $\Psi \vdash A \le B$;
    \item If $\Gm \Vdash e \Lto A \redto \nil$ then $\Psi \vdash e \Lto A$;
    \item If $\Gm \Vdash e \To_a \jg \redto \nil$ for any $\jg$, then there exists $A$
        s.t. $\Psi \vdash e \To A$;
    \item If $\Gm \Vdash \appInfAlg{A}{e} \redto \nil$ for any $\jg$, then there exists $C$
        s.t. $\Psi \vdash \appInf{A}{e}{C}$.
\end{enumerate}
\end{corollary}

@@

\begin{theorem}[Completeness]
If \emph{wf }$\Gm$ and $\Gm\sto\Om$ and $\Om\redto\nil$, then $\Gm \redto \nil$.
\label{thm:completeness}
\end{theorem}

@@

The following corollary is derived immediately from Theorem~\ref{thm:completeness}.
\begin{corollary}[Completeness, single judgment form]
Given \emph{wf }$\Psi$ and $\Gm = \Psi$:
\begin{enumerate}
    \item If $\Psi \vdash A \le B$ then $\Gm \Vdash A \le B \redto \nil$;
    \item If $\Psi \vdash e \Lto A$ then $\Gm \Vdash e \Lto A \redto \nil$;
    \item If $\Psi \vdash e \To A$ then $\Gm \Vdash e \To_a 1 \le 1 \redto \nil$;
    \item If $\Psi \vdash \appInf{A}{e}{C}$ then $\Gm \Vdash \appInfAlg{A}{e}[a][1 \le 1] \redto \nil$.
\end{enumerate}
\end{corollary}

@@

We have proven this theorem by a lexicographic group of induction measures\\
$\langle |\Gm|_e, |\Gm|_\Leftrightarrow, |\Gm|_\forall, |\Gm|_{\al}, |\Gm|_\to + |\Gm| \rangle$
on the worklist $\Gm$.
$|\cdot|_e$ and $|\cdot|_\Leftrightarrow$ measure the total ``size'' of terms
and the total ``difficulty'' of judgments, respectively;
$|\cdot|_\forall$ and $|\cdot|_\to$ count the total number of
universal quantifiers and function types, respectively;
$|\cdot|_{\al}$ counts the number of existential variables in the worklist.

@@

Combining all the three main results, we know that the declarative system is decidable,
with the help of our algorithm.
\begin{corollary}[Decidability of Declarative Typing]
Given \emph{wf }$\Om$, it is decidable whether $\Om\redto\nil$ or not.
\end{corollary}
\subsection{Abella}
